### 2017-02-26 2017mergingmerges/section/03-Definition.tex
Flab on what an update is

All instructions include a $\Next$ field which is a pair of the label of the next instruction to execute, as well as a map of heap $\Var$ to $\Exp$ which is used to update the heap. The map of update expressions is attached directly to instructions to make the fusion algorithm easier to specify, in contrast to a presentation with a separate @update@ instruction.

>>>>

All instructions include a $\Next$ field which is a pair of the label of the next instruction to execute, as well as a list of $\Var \times \Exp$ bindings used to update the heap. The list of update bindings is attached directly to instructions to make the fusion algorithm easier to specify, in contrast to a presentation with a separate @update@ instruction.
